### 2016-06-16 motivation.tex
Edits.

\label{fig:motiv-eg-1-hb}
\caption{$\hbZ$ arrows allowed by SI (solid) and RC (solid and dashed)
isolation levels for the example in Fig.~\ref{fig:motiv-eg-1}. Each
arrow represents $\hbZ$ relationship between all operations of `Wd2'
and operations in `Wd1' that follow the arrow head. Letters R, W and C
stand for read, write and commit, respectively.}
\end{figure}

@@

We have thus far assumed an SC store that, in the absence of
transactions with special isolation requirements, makes effects of an
operation to be immediately visible to subsequent operations. Thus,
the natural behavior of SC store to totally order all operations w.r.t
$\hbZ$ relation could be in conflict with the constraints imposed by
weak isolation. To meet the requirements of weaker isolation levels,
say RC, the store has to adapt itself to \emph{hide} the effects of
concurrent transactions until they are committed. Once committed
though, the effects need to be immediately and perennially visible to
subsequent operations. This semantics of an SC store can be built into
the reasoning framework leading to a proof system tailor-made for such
stores. However, for the reasoning framework to be useful across the
stores, it has to be parametric over store consistency semantics, and
should be able to reconcile conflicts betweenconsistency and isolation
constraints. Later sections demonstrate how our reasoning framework
makes this possible.

>>>>

\caption{$\hbZ$ arrows allowed by SI (solid) and RC (solid and dashed)
isolation levels for the example in Fig.~\ref{fig:motiv-eg-1}. Each
arrow represents $\hbZ$ relationship between all operations of `Wd2'
and operations in `Wd1' that follow the arrow head. Letters R, W and C
stand for read, write and commit, respectively.}
\label{fig:motiv-eg-1-hb}
\end{figure}

@@

We have thus far assumed an SC store that, in the absence of
transactions with special isolation requirements, makes effects of an
operation to be immediately visible to subsequent operations. The
natural behavior of SC store to totally order all operations w.r.t
$\hbZ$ relation could be in conflict with the constraints imposed by
weak isolation. To meet the requirements of weaker isolation levels,
say RC, the store has to adapt itself to \emph{hide} the effects of
concurrent transactions until they are committed. Once committed
though, the effects need to be immediately and perennially visible to
subsequent operations. This semantics of an SC store can be built into
the reasoning framework leading to a proof system tailor-made for such
stores. However, for the reasoning framework to be useful across the
stores, it has to be parametric over store consistency semantics, and
should be able to reconcile conflicts betweenconsistency and isolation
constraints. Later sections demonstrate how our reasoning framework
makes this possible.
